---
title: "p8105_hw1_jer2243"
author: "Juliet Rowe"
date: "2023-09-18"
output: github_document
---
### PROBLEM 1 ###

## Load package and dataset

```{r}
library("moderndive")

data("early_january_weather")

```


## Data description

```{r}
?early_january_weather

nrow(early_january_weather)
ncol(early_january_weather)

mean_temp <- mean(early_january_weather$temp)
print(mean_temp)
```
#The "early_january_weather" dataset contains 358 rows representing hourly measurements
and 15 variables. Variables include "origin", "year,month,day,hour", "temp", "dewp", "humid",
"wind_dir", "wind_speed", "wind_gust", "precip", "pressure", "visib", and "time_hour".
#The mean temperature equals 39.58212 degreed F.

## Scatterplot creation and export

```{r cars}
library(ggplot2)
gg <- ggplot(data=early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()

ggsave("scatterplot_temp_vs_time.png", plot=gg, width=10, height=7)
```
#Overall, temperatures rose throughout the month of January. Throughout each day, the plot generally shows temperatures dropping during the night and rising during the day. Humidity levels seemed to peak around January 11-14.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
