---
title: "p8105_hw1_jer2243"
author: "Juliet Rowe"
date: "2023-09-18"
output: github_document
---
# Problem 1

## Load package and dataset

```{r}
library("moderndive")
library(tidyverse)

data("early_january_weather")

```


## Data description

```{r}
?early_january_weather

nrow(early_january_weather)
ncol(early_january_weather)

mean_temp <- mean(pull(early_january_weather, temp))
print(mean_temp)
```
The "early_january_weather" dataset contains 358 rows representing hourly measurements
and 15 variables. Variables include "origin", "year,month,day,hour", "temp", "dewp", "humid",
"wind_dir", "wind_speed", "wind_gust", "precip", "pressure", "visib", and "time_hour".
The mean temperature equals 39.58212 degrees Fahrenheit.

## Scatterplot creation and export

```{r cars}
library(ggplot2)
gg <- ggplot(data=early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()

ggsave("scatterplot_temp_vs_time.png", plot=gg, width=10, height=7)
```
Overall, temperatures rose throughout the month of January. Throughout each day, the plot generally shows temperatures dropping during the night and rising during the day. Humidity levels seemed to peak around January 11-14.

# Problem 2

## Variable creation
```{r}
  random <- rnorm(10, sd=1)
  logical <-  random > 0
  character <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
  factor <- factor(rep(c("A", "B", "C"), length.out=10))
```

## Load tidyverse and create dataframe
```{r}
library(tidyverse)

hw1_df=tibble(
  random,
  logical,
  character,
  factor
)
```

## Taking the mean of each variable
```{r}
mean_random <- mean(pull(hw1_df, random))
mean_logical <- mean(pull(hw1_df, logical))
mean_character <- mean(pull(hw1_df, character))
mean_factor <- mean(pull(hw1_df, factor))
```
Mean of the random variable = -0.0623
Mean of the logical variable = 0.4
Mean of the character and factor variables cannot be calculated.

## Applying the as.numeric function to the logical, character, and factor variables.
```{r}
as.numeric(logical)
as.numeric(character)
as.numeric(factor)
```
Applying this function to the logical variable codes "FALSE" as 0 and "TRUE" as 1. This explains how the mean of the logical variable came out to be 0.6. Applying this function to the character variable just causes all of the values to be missing, or "NA", explaining why taking the mean results in an error, as the characters cannot be converted to a number. Finally, the factor variable takes on the value of its level - in this case, 1, 2, or 3, since we coded it to have 3 levels. 
